Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-10-20 ms.tex
added example PSFs from OTIS.

\subsection{Pre-amp Reset Offsets}\label{sec:preAmp}

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the photon noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source usually gives the best precision light curves
\end{itemize}

We also found reduction steps that had very little impact on the final photometric precision including
\begin{itemize}
	\item IPC corrections ($\lesssim 0.01$ ppm)
	\item Flat-fielding ($\lesssim 0.3$ ppm)
	\item 
\end{itemize}
We summarize the lessons from the tests here.

There are also some lessons learned from CV3 tests on which corrections have small effects on the final measured precision.
These corrections are:
\begin{itemize}
	\item 
\end{itemize}

%\begin{figure*}
%\gridline{\fig{sample_img.pdf}{0.3\textwidth}{Red Figure}
%          \fig{sample_red.png}{0.3\textwidth}{Green Figure}
%          }
%\caption{Two figures side by side.\label{fig:gridFig}}
%\end{figure*}

>>>>

\subsection{Pre-amp Reset Offsets from the Lockheed CV Test}\label{sec:preAmp}

@@

After experimenting with these configurations, we find the following pipeline steps are important:
\begin{itemize}
	\item Fitting a line up the ramp gives superior results to subtracting the last and first pairs of read (as expected by reducing the photon noise)
	\item Centering the aperture with the central spot inside the hexagon is important to conserve the flux within the aperture
	\item Row-by-row subtraction (along the detector's fast-read direction) gives superior background subtraction to traditional aperture photometry (using the mean or robust average value in a background annulus)
	\item Aperture sizes for the source at ~70 pixels, outside the hexagon, gave the best precisions
	\item An annulus aperture on the source (including the inner and outer edges of the hexagonal PSF) usually gives the best precision light curves
\end{itemize}

We also found reduction steps that had very little impact on the final photometric precision including
\begin{itemize}
	\item IPC corrections ($\lesssim 0.01$ ppm)
	\item Flat-fielding ($\lesssim 0.3$ ppm)
\end{itemize}
We summarize the lessons from the tests here.

\subsection{OTIS Tests}

A series of NIRCam stability tests were carried out while the entire JWST telescope system was placed in a tall vacuum chamber at NASA Johnson.
During these tests, there were two configurations 1) the "half pass" tests where lamp sources within the optical system and 2) "pass and a half" tests where the a lamp source within the optical system bounces light off the secondary, primary, flat mirrors mounted on the chamber's ceiling and then through the entire telescope and instrument chain.

The OTIS testing included a time series mode similar to the grism time series template used in orbit for transiting planets.
Figure \ref{fig:otisPSFs} shows the point spread functions for the OTIS tests.

\begin{figure*}
\gridline{\fig{wlp8_otis_psf.pdf}{0.49\textwidth}{WLP8 Image}
          \fig{grism_otis_psf.pdf}{0.49\textwidth}{Grism Image}
          }
\caption{Example OTIS  images obtained simultaneously during the long duration time series.
Due to the OTIS optics set up, the short wavelength WLP8 image does not nearly represent the hexagonal PSF from CV3 or flight.}\label{fig:otisPSFs}
\end{figure*}

\subsection{GL Dewar Tests}
